%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Alicia Sykes CV LaTeX Template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{resume-format}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength\fboxsep{10pt}%

\begingroup
  \hypersetup{
    colorlinks=true,
    linkcolor=white,
    urlcolor=white,
    citecolor=white,
    pdfborder={0 0 0}
  }%

\noindent
\colorbox{headerbg}{
  \parbox{\dimexpr\textwidth-2\fboxsep}{
    \color{white} %
    \begin{center} %
      \headerfirstnamestyle{ Alicia } %
      \headerlastnamestyle{  Sykes }\\[2mm] %
      \faEnvelope~\href{mailto:hello@aliciasykes.com}hello@aliciasykes.com %
      \quad|\quad %
      \faMapMarker~London, UK %
      \quad|\quad %
      \faLink~\href{ https://github.com/lissy93 }{ https://github.com/lissy93 } %
    \end{center} %
  }
}
\endgroup
\vspace{2mm} %


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Statement
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{cvpersonalstatement}
  \item { I\textquotesingle{}m a builder at heart. I care about clean, simple software that\textquotesingle{}s fast,
secure, accessible—and actually helps people.
Over the years, I\textquotesingle{}ve led teams, shipped products used by millions,
modernised ageing systems, and helped engineers grow.
I believe in open source, protecting user privacy, and leaving things better
than I found them.
I like working with kind, curious people who want to do great work and have a
little fun along the way.
 }
\end{cvpersonalstatement}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Experience}
\begin{cventries}
    \cventry
    { Staff Software Engineer }
    { loveholidays }
    {}
    { November 2024 – Present }
    {\begin{cvitems}
        \item { Led accessibility strategy ahead of the European Accessibility Act by building lova11y, a site-wide scanning tool that logs and categorises violations into BigQuery and Looker, enabling measurable progress across teams. }
        \item { Contributed to core web infrastructure (Kubernetes, Terraform), worked closely with vendors like Fastly and DataDome, and delivered improvements in site performance and reliability. }
        \item { As learning champion, I created resources and pathways to foster continuous learning, mentoring, and upskilling across the engineering org. }
    \end{cvitems}}
    \cventry
    { Principal Engineer }
    { AND Digital }
    {}
    { August 2022 – October 2024 }
    {\begin{cvitems}
        \item { Led architecture and development for a high-scale white-labelled mobile app for Frasers Group, achieving 1M+ downloads and a 4.8/5 rating on app stores (React Native). }
        \item { Delivered strategic technical leadership across multiple client projects including Lloyds Bank and International SOS, driving large-scale migrations to modern, maintainable stacks. }
        \item { Mentored and upskilled a team of 8–12 engineers through structured mini-projects, paired programming, and technical coaching, fostering a high-growth culture. }
        \item { Established and hosted a bi-weekly engineering guild attended by 40+ engineers, sharing best practices in performance, accessibility, testing, and architecture. }
        \item { Acted as a bridge between delivery and engineering excellence, ensuring long-term code quality and platform resilience without compromising speed. }
    \end{cvitems}}
    \cventry
    { VP of Frontend Engineering }
    { Galaxy }
    {}
    { June 2020 – May 2022 }
    {\begin{cvitems}
        \item { Directed frontend engineering for Galaxy\textquotesingle{}s flagship OTC trading platform, enabling over \$1B in trading volume with enterprise-grade performance and reliability. }
        \item { Architected and led a full-stack modernization of legacy codebases, improving app load times by 50\% and significantly reducing tech debt. }
        \item { Oversaw and scaled frontend engineering strategy, standards, and execution across multiple teams, including hiring, mentoring, and tech governance. }
        \item { Shipped high-quality features rapidly through close cross-functional collaboration. Increasing team velocity by 30\% through improved CI/CD processes and tooling. }
        \item { Advocated for open standards, accessibility, and performance as core pillars of engineering success. }
    \end{cvitems}}
    \cventry
    { Contract Software Engineer Lead }
    { Freelance }
    {}
    { January 2018 – June 2020 }
    {\begin{cvitems}
        \item { Acted as engineering lead on high-impact React Native projects including Shell Recharge, driving delivery from design to deployment across platforms. }
        \item { Built a performant, scalable component library from scratch for a UK fintech startup, establishing strong frontend architecture and design consistency. }
        \item { Delivered a full-stack IoT dashboard for Machine Max, visualizing real-time CO2 and idling metrics from edge devices (Raspberry Pi + cloud stack). }
        \item { Consistently embedded in client teams as a trusted lead, providing architecture reviews, CI/CD pipeline improvements, and technical mentorship. }
    \end{cvitems}}
    \cventry
    { Developer }
    { Accenture }
    {}
    { May 2014 – January 2019 }
    {\begin{cvitems}
        \item { Took lead on the 3D/AR work for the B\&Q bathroom planner (Angular, A-Frame) }
        \item { Lead a team of apprentices on the Accenture UKI Innovation Programme (Google Glass, React, D3.js) }
        \item { Ran sessions on coding best practices, testing and observability for engineers across the business }
        \item { Headed up the pair programming initiative within Accenture Digital and their clients }
        \item { Also supported with the roll-out of Universal Credit (Java), Boots NHS Prescriptions integration (Node.js), E.ON Next Smart Meter portal (React) and the Post Office Kiosk Terminal }
    \end{cvitems}}
\end{cventries}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Education}
\begin{cventries}
    \cventry
    { BSc in Computer Science }
    { Oxford Brookes }
    {}
    {}
    {Grade: 1st Class Honors. Winner of Best Final Year Project Prize. President of Computing Society.}
\end{cventries}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Skills}
\vspace{0.5mm}  % match Stats/Awards
\begin{cvskills}
  \cvskill{ Frontend }{ React, Svelte, TypeScript }
  \cvskill{ Backend }{ Go, Rust, Node.js, Python, Java, PHP }
  \cvskill{ Mobile }{ Kotlin, Swift, React Native, Flutter }
  \cvskill{ DevOps }{ Ansible, Kubernetes, Terraform }
  \cvskill{ Obs/Mon }{ Prometheus, ELK stack, OpenTelemetry, Grafana }
  \cvskill{ CI/CD }{ Argo CD, GitHub Actions }
  \cvskill{ Cloud }{ Vercel, Netlify, GCP, Azure }
  \cvskill{ Databases }{ PostgreSQL, SQLite, Redis, MySQL, MongoDB }
\end{cvskills}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements Statistics
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Stats}
\vspace{0.5mm}
\begin{cvachievements}
\setlength{\itemsep}{0mm}
  \item { Top 100 GitHub developer worldwide (70k+ stars) \href{ https://gitstar-ranking.com/Lissy93 }{\scriptsize\color{lightgray}\faLink} }
  \item { 10M+ Docker pulls for my open-source projects \href{ https://hub.docker.com/u/lissy93 }{\scriptsize\color{lightgray}\faLink} }
  \item { 10+ global hackathon wins, demonstrating rapid innovation \href{ https://notes.aliciasykes.com/p/0s5s3uOtKj }{\scriptsize\color{lightgray}\faLink} }
  \item { 1M+ lines of code authored, maintainer of 100+ repos, powering 1M+ annual unique users \href{ https://codestats.net/users/alicia }{\scriptsize\color{lightgray}\faLink} }
  \item { 10k+ subscribers on DEV.to blog, and 5k+ followers on X, GitHub, LinkedIn \href{ https://dev.to/lissy93 }{\scriptsize\color{lightgray}\faLink} }
  \item { Top 1\% contributor on StackOverflow \href{ https://stackoverflow.com/users/979052/alicia-sykes }{\scriptsize\color{lightgray}\faLink} }
\end{cvachievements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Awards}
\vspace{0.5mm}
\begin{cvachievements}
\setlength{\itemsep}{0mm}
  \item { \textbf{ Open UK Honours List (2025) } - Recognised for outstanding contributions to the tech and open-source sector \href{ https://openuk.uk/honours/ }{\scriptsize\color{lightgray}\faLink} }
  \item { \textbf{ GitHub Accelerator Alumni } - Selected among 10 developers (Microsoft M12 partnership) to launch AI-security tooling \href{ https://accelerator.github.com/ }{\scriptsize\color{lightgray}\faLink} }
  \item { \textbf{ Open UK Honours List (2024) } - Honoured for leadership and impact in open-source communities \href{ https://openuk.uk/community/openuk-honours-lists/2024-honours-list }{\scriptsize\color{lightgray}\faLink} }
  \item { \textbf{ Best Comp Sci Project } - Awarded by Oxford British Computer Society \href{ https://oxon.bcs.org/2016/06/27/annual-student-prizes-2016/ }{\scriptsize\color{lightgray}\faLink} }
\end{cvachievements}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Projects}
\vspace{0.5mm}
\begin{cvachievements}
  \setlength{\itemsep}{0mm}
  \item {
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
      \href{ https://dashy.to }{\textbf{ Dashy }} 
      - The self-hosted startpage for servers \href{ https://dashy.to }{\scriptsize\color{lightgray}\faLink}
      & 
      \href{https://github.com/lissy93/dashy}{\faGithub\ lissy93/dashy} \\
    \end{tabular*}
  }
  \item {
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
      \href{ https://web-check.xyz }{\textbf{ Web-Check }} 
      - OSINT website scanner \href{ https://web-check.xyz }{\scriptsize\color{lightgray}\faLink}
      & 
      \href{https://github.com/lissy93/web-check}{\faGithub\ lissy93/web-check} \\
    \end{tabular*}
  }
  \item {
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
      \href{ https://adguardian.as93.net/ }{\textbf{ AdGuardian }} 
      - CLI DNS and traffic monitoring in the terminal \href{ https://adguardian.as93.net/ }{\scriptsize\color{lightgray}\faLink}
      & 
      \href{https://github.com/lissy93/AdGuardian-Term}{\faGithub\ lissy93/AdGuardian-Term} \\
    \end{tabular*}
  }
  \item {
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
      \href{ https://digital-defense.io/ }{\textbf{ Digital Defense }} 
      - Comprehensive personal security assessment tool \href{ https://digital-defense.io/ }{\scriptsize\color{lightgray}\faLink}
      & 
      \href{https://github.com/lissy93/personal-security-checklist}{\faGithub\ lissy93/personal-security-checklist} \\
    \end{tabular*}
  }
  \item {
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l r}
      \href{ https://domain-locker.com/ }{\textbf{ Domain Locker }} 
      - All-in-one domain management and security platform \href{ https://domain-locker.com/ }{\scriptsize\color{lightgray}\faLink}
      & 
      \href{https://github.com/lissy93/domain-locker}{\faGithub\ lissy93/domain-locker} \\
    \end{tabular*}
  }
\end{cvachievements}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Footer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10mm}
\begin{center}
    \tiny\color{lightgray}
    Resume built with LaTeX, view source at
    \href{https://github.com/lissy93/cv}{ github.com/lissy93/cv }.
    Licensed under MIT (C)
    \href{https://aliciasykes.com}{ Alicia Sykes } 2025
\end{center}
\ 
\end{document}